Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-05 popl24/scratch.tex
checkpoint

\begin{lemma}
  \label{lemma-gmw-frame}
  If $\sep{\progtt(\prog_2)}{Y}{Z}$ and $\sep{\progtt(\prog_1)}{X}{Y}$ for
  $X \not\in \vars(\prog_2)$ then $\sep{\progtt(\prog_1;\prog_2)}{X}{Z}$. 
\end{lemma}

@@

\begin{lemma}[GMW Gate Invariant]
  \label{lemma-preservation-gmw}
  Given well-typed $\prog_1;E[\mathit{gate}(\ttt{g},v_1,v_2)]$ and certified $\mathit{gate}$ where
  for some $\ttt{g1}$ and $\ttt{g2}$, :
  $$
  \begin{array}{lcr}
   v_1 &=& \ttt{\{c1 = v[1,g1out]; c2 = v[2,g1out]\}}\\
   v_2 &=& \ttt{\{c1 = v[1,g2out]; c2 = v[2,g2out]\}}
  \end{array}
  $$
  and let:
  $$
  \config{\prog_1}{E[\mathit{gate}(\ttt{g},v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[\ttt{\{c1 = v[1,gout]; c2 = v[2,gout]\}}]}
  $$
  If we have the following precondition, where $\iov(\prog_1) = S \cup V$:
  $$
  \sep{\progd(\prog_1)}{(S_{\{2\}} \cup V_{\{2\}})}{(S_{\{1\}} \cup V_{\{1\}})}
  $$
  then we have as a postcondition:
  $$
  \sep{\progd(\prog_1)}{(S_{\{2\}} \cup V_{\{2\}} \cup \{ \ttt{v[2,gout]} \})}{(S_{\{1\}} \cup V_{\{1\}} \cup \{ \ttt{v[1,gout]} \})}
  $$
\end{lemma}

@@

\begin{definition}[GMW Encode Certification]
  Let $\mathit{encode}$ be an encoding function, and let:
  $$
  \config{\varnothing}{\ttt{encode(s1,s2)}} \redxs
  \config{\prog}{\ttt{\{shares1 = }v_1\ttt{; shares2 = }v_2\ttt{\}}}
  $$
  where:
  $$
  \begin{array}{rcl}
    v_1 &=& \ttt{\{ c1 = v[1,s1out]; c2 = v[2,s1out] \}}\\
    v_2 &=& \ttt{\{ c1 = v[1,s2out]; c2 = v[2,s2out] \}}
  \end{array}
  $$
  Then $\mathit{encode}$ is \emph{certified} iff each of the following conditions hold:
  \begin{enumerate}[\hspace{5mm}i.]
  \item $\sep{\progtt(\prog)}{\ttt{\{ s[1,s1] \}}}{\ttt{\{ v[2,s1out], v[2,s2out] \}}}$
  \item $\sep{\progtt(\prog)}{\ttt{\{ s[2,s2] \}}}{\ttt{\{ v[1,s1out], v[1,s2out] \}}}$
  \item All $x \in \vars(\prog)$ are distinguished by $\ttt{in1}$ or $\ttt{in2}$. 
  \end{enumerate}
\end{definition}

>>>>

\begin{lemma}
  \label{lemma-gmw-frame}
  If $\sep{\progtt(\prog_1;\prog_2)}{Y}{V}$ for $V \in \vdefs(\prog_2)$ and $\sep{\progtt(\prog_1)}{X}{Y}$ for
  $X \not\in \vars(\prog_2)$ then $\sep{\progtt(\prog_1;\prog_2)}{X}{V}$. 
\end{lemma}
\begin{proof}
  By assumption and Lemma \ref{lemma-sepjoin}, for all
  $\store^1,\store^2 \in \runs(\prog_1;\prog_2)$ we have $\store^1_Y
  \cap \store^2_V \subseteq \store$ for some $\store_a \in
  \runs(\prog_1;\prog_2)$ and $\store^1_X \cap \store^2_Y \subseteq
  \store$ for some $\store_b \in \runs(\prog_1;\prog_2)$.  Thus, since
  we assume $X \not\in \vars(\prog_2)$ we have $\store_a \cap \store_b
  \in \runs(\prog_1;\prog_2)$ and $\store^1_X \cap \store^2_V =
  \store_a \cap \store_b$, obtaining the result by
  \ref{lemma-sepjoin}.
\end{proof}

@@

\begin{lemma}[GMW Gate Invariant]
  \label{lemma-preservation-gmw}
  Given well-typed $\prog_1;E[\mathit{gate}(\ttt{g},v_1,v_2)]$ for certified $\mathit{gate}$ where
  for some $\ttt{g1}$ and $\ttt{g2}$, :
  $$
  \begin{array}{lcr}
   v_1 &=& \ttt{\{c1 = v[1,g1out]; c2 = v[2,g1out]\}}\\
   v_2 &=& \ttt{\{c1 = v[1,g2out]; c2 = v[2,g2out]\}}
  \end{array}
  $$
  and let:
  $$
  \config{\prog_1}{E[\mathit{gate}(\ttt{g},v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[\ttt{\{c1 = v[1,gout]; c2 = v[2,gout]\}}]}
  $$
  If we have the following precondition, where $\iov(\prog_1) = S \cup V$:
  $$
  \sep{\progd(\prog_1)}{(S_{\{2\}} \cup V_{\{2\}})}{(S_{\{1\}} \cup V_{\{1\}})}
  $$
  then we have as a postcondition:
  $$
  \sep{\progd(\prog_1;\prog_2)}{(S_{\{2\}} \cup V_{\{2\}} \cup \{ \ttt{v[2,gout]} \})}{(S_{\{1\}} \cup V_{\{1\}} \cup \{ \ttt{v[1,gout]} \})}
  $$
\end{lemma}

@@

\begin{definition}[GMW Encode Certification]
  \label{definition-gmwencode-certification}
  Let $\mathit{encode}$ be an encoding function, and let:
  $$
  \config{\varnothing}{\ttt{encode(s1,s2)}} \redxs
  \config{\prog}{\ttt{\{shares1 = }v_1\ttt{; shares2 = }v_2\ttt{\}}}
  $$
  where:
  $$
  \begin{array}{rcl}
    v_1 &=& \ttt{\{ c1 = v[1,s1out]; c2 = v[2,s1out] \}}\\
    v_2 &=& \ttt{\{ c1 = v[1,s2out]; c2 = v[2,s2out] \}}
  \end{array}
  $$
  Then $\mathit{encode}$ is \emph{certified} iff each of the following conditions hold:
  \begin{enumerate}[\hspace{5mm}i.]
  \item $\sep{\progtt(\prog)}{\ttt{\{ s[1,s1],  v[1,s1out], v[1,s2out] \}}}{\ttt{\{ s[2,s2], v[2,s1out], v[2,s2out] \}}}$
  \item All $x \in \vars(\prog)$ are distinguished by $\ttt{in1}$ or $\ttt{in2}$. 
  \end{enumerate}
\end{definition}

\begin{lemma}[GMW Encode Invariant] 
  Given well-typed $\prog_1;E[\mathit{encode}\ttt{(s1,s2)}]$ for certified $\mathit{encode}$, let:
  $$
  \config{\prog_1}{E[\mathit{encode}(\ttt{s1},\ttt{s2})]} \redxs
  \config{\prog_1;\prog_2}{E[\ttt{\{shares1 = }v_1\ttt{; shares2 = }v_2\ttt{\}}]}
  $$
  If we have the following precondition, where $\iov(\prog_1) = S \cup V$:
  $$
  \sep{\progd(\prog_1)}{(S_{\{2\}} \cup V_{\{2\}})}{(S_{\{1\}} \cup V_{\{1\}})}
  $$
  then we have as a postcondition, where $\iov(\prog_1;\prog_2) = S' \cup V'$:
  $$
  \sep{\progd(\prog_1;\prog_2)}{(S'_{\{2\}} \cup V'_{\{2\}})}{(S'_{\{1\}} \cup V'_{\{1\}})}
  $$
\end{lemma}

\begin{proof}
  By Definition \ref{definition-gmwencode-certification} we have:
  $$\sep{\progtt(\prog)}{\ttt{\{ s[1,s1],  v[1,s1out], v[1,s2out] \}}}{\ttt{\{ s[2,s2], v[2,s1out], v[2,s2out] \}}}$$
  Since we assume that secrets are in uniform and independent marginal distributions a priori,
  and $\vars(\prog_1) \cap \vars(\prog_2)$ by condition (ii) of
  Definition \ref{definition-gmwencode-certification}, thus by assumption and Lemma \ref{lemma-separation}:
  $$\sep{\progtt(\prog)}{(S_1 \cup V_1 \cup \ttt{\{ s[1,s1],  v[1,s1out], v[1,s2out] \}})}{(S_2 \cup V_2 \cup \ttt{\{ s[2,s2], v[2,s1out], v[2,s2out] \}}}$$
  which was to be proven.
\end{proof}
